\section {
  What is the original meaning of the world Paradigm?
}

Paradigm is a set of methods which can be defined and applied repetitively. In
some word it also means a pattern.


\section {
  How do objects interact with each other?
}

Objects interact by calling each others methods. When expected parameters of
any method is combined with a method it becomes a message. One object will
request another object by passing a message to it. A receiver object will
process given request via performing actions and return its results.

\section {
  How are messages different from procedure calls?
}

Messages are different than procedure calls in many ways. My most remarkable
observation is that when any procedure is called it is called directly. Various
calls to single procedure are not different. Whereas message is passed to
individual agents (objects). Each agent will expect messages differently and
will perform actions differently.

\section {
  What is the name applied to describe an algorithm that an object uses to
  respond to a request?
}

Method resolution.

\section {
  Why does the object-oriented approach naturally imply a high degree of
  information hiding?
}

Because it fundamentally abstracts an implementation with one who instructed to
perform it.

\section {
  What is a class? How are classes linked to behavior?
}

Class is a set of methods related to an entity. Methods are responsible for
performing actions to get a requested result. Definition of this methods are
different from entities to entities. How they react when it is called is
similar to how human behaves according to various situations.

\section {
  What is a class inheritance hierarchy? How is it linked to classes and
  behavior?
}

Class inheritance is a way to inherit behaviours from parent class. A child
class do not implement that behaviour, but it is capable of react on whatever
behavior is defined by its parent.

\section {
  What does it mean for one method to override another method from a parent
  class?
}

A child class implements that method in its own way. This can be different form
what implementation a parent class has. Signature of this method is exactly
same with a signature of method implemented at parent class.

\section {
  What are the basic elements of process-state model of computation?
}

New, Ready, Waiting, Terminated.

\section {
  How does the object-oriented model of computation differ from the process
  state model?
}
